\documentclass{../Template/my_cv}
\ifxetex
  \usepackage{fontspec}
  \setmainfont{Times New Roman}
\fi
\usepackage{multirow}
\normalsize

\begin{document}

\newlength{\colOne}
\setlength{\colOne}{\dimexpr (\textwidth-24pt)/10 \relax}
\newlength{\colTwo}
\setlength{\colTwo}{\dimexpr (\textwidth-24pt)/3 \relax}



\myName{Yadong}{Jiang}

%Personal Data
\section{Personal Data}

\noindent\hspace{24pt}
\begin{tabular}{p{\colOne} p{\colTwo} p{\colOne} p{\colTwo}}
Nationality: & Chinese & Address: & \multirow{4}{*}{\shortstack[l]{Chenggong Hongshuling 3rd Building\\ Chenhui East Road, 1501 \\ Jinjiang district, Chengdu, Sichuan\\ P.R. China}}\\

Birthday: & 1990 Oct & & \\

Gender: & Male & & \\

Email: & \href{mailto:yadong.jiang@iusspavia.it}{yadong.jiang@iusspavia.it} & & \\

Phone: & (+351) 910-275-117 & & \\

\end{tabular}


%Education
\section{Education}

\period{
    Sep. 2014 $\sim$ Current
}{
    \textbf{Ph.D candidate}, Earthquake Engineering and Engineering Seismology, ROSE Programme\\
    
    Istituto Universitario di Studi Superiori di Pavia (IUSS), Pavia, Italy\\
    
    Thesis: Seismic Assessment of Composite Frames with Concrete-Filled Steel Tube Columns\\
    
    Advisors: Jose Miguel Castro and Ricardo Monteiro
}

\period{
    Sep. 2012 $\sim$ May. 2014
}{
    \textbf{Master of Science}, Earthquake Engineering and Engineering Seismology, ROSE Programme\\
    
    Istituto Universitario di Studi Superiori di Pavia (IUSS), Pavia, Italy\\
    
    Thesis: Experimental and Numerical Behavior Assessment of Rubberized Concrete Filled Steel Tube\\
    
    Advisors: Jose Miguel Castro and Ricardo Monteiro
}

\period{
    Sep. 2008 $\sim$ Jun. 2012
}{
    \textbf{Bachelor}, Civil Engineering\\
    
    Tongji University, Shanghai, P.R. China\\
    
    GPA: 4.23/5.0 (five-level grading system)
}
%Research experience
\section{Research \& Professional Experiences}

\period{
    Feb. 2016 $\sim$ May. 2016
}{
    \textbf{Research Assistant}, Department of Civil and Environmental Engineering (CEE)\\

    Hong Kong Polytechnic University, Hong Kong\\
    
    \hangindent=61pt
    Project Title: Application of Polygonal High Strength Concrete-filled composite Column in Seismic-resistant Buildings in Hong Kong\\
    
    Supervisor: Tak-Ming Chan
}

\period{
    Jan. 2014 $\sim$ Feb. 2015
}{
    \textbf{Research Assistant}, Faculty of Engineering\\
    University of Porto, Porto, Portugal\\
    
    \hangindent=55pt
    Project Title: Recycling \& Seismic Protection: Sustainable High Performance Concrete-Filled Steel Tubular (CFST) Columns for Seismic Areas\\
    
    Supervisor: Jose Miguel Castro
}

\period{
    Feb. 2012 $\sim$ Apr. 2012
}{
    \textbf{Internship}, Metro tunnel crack check, Shanghai, P.R. China    
}

%Skills
\section{Skill Sets}

\def\arraystretch{1.5}
\begin{tabular}{p{\dimexpr \colOne+\colTwo \relax} p{\dimexpr \colOne+\colTwo \relax}}
    \multicolumn{2}{l}{\textbullet\ ABAQUS / OpenSees / RUAUMOKO/ SeismoStruct Modelling and Analysising} \\
    
    \textbullet\ OpenSees Material Developing & \textbullet\ Matlab Scripting \\

    \textbullet\ Python / C++ / C\# language Programming & \textbullet\ Auto CAD Engineering Drawing\\

    \textbullet\ Word / Excel / PowerPoint Processing & \textbullet\ \LaTeX \hspace{2pt} Basics
\end{tabular}


%Scholarships
\section{Scholarships}

\period{
    Sep. 2014 $\sim$ Aug. 2017
}{
    IUSS Ph.D. Scholarship
}

\period{
    Sep. 2012 $\sim$ May. 2014
}{
    UME/Tongji MSc Scholarship
}

\period{
    Sep. 2010 $\sim$ Sep.2012
}{
    Tongji University Scholarship
}

%Conference
\section{Conferences \& Workshops}

\period{
  Sep. 2017
} {
  8th European Conference on Steel and Composite Structures (Eurosteel 2017)\\

  Copenhagen, Denmark\\

  Oral Presentation: Numerical modelling of circular CFST members and assessment of multi-axial stress state effects\\

  Oral Presentation: Experimental characterisation of the flexural behaviour of rubberized concrete-filled steel tubular members
}

\period{
  Jun. 2017
} {
  OpenSees Days Europe 2017\\

  Porto, Portugal\\
  Oral Presentation:  Numerical modelling of concrete-filled steel tubular members in opensees
}

\period {Jan. 2017} {
  16th World Conference on Earthquake Engineering (WCEE16)\\

  Santiago, Chile\\

  Oral Presentation: Experimental and numerical assessment of the behaviour of RuCFST members under monotonic and cyclic bending
}

\period {Nov. 2015} {
  Steel-Earth Workshop\\
  Coimbra, Portugal\\
  Oral Presentation: Experimental and Numerical Assessment of the Behaviour of Rubberized Concrete Filled Steel Tubes
}


\period {Jul. 2015} {
  8th International Conference on Behavior of Steel Structures in Seismic Areas (STESSA15)\\

  Shanghai, China\\
  
  Oral Presentation: Experimental assessment of the behaviour of rubberized concrete filled steel tube members
}

\period {Jul. 2014} {
  OpenSees Days Portugal\\

  Porto, Portugal \\

  Oral Presentation: Opensees as an engine for web-based applications
}

%Publication
\section{Publications}

\subsection{Journal Papers}

\bitem{
A. Silva, Y. Jiang, J.M. Castro, N. Silvestre, and R. Monteiro. Monotonic and cyclic flexural behaviour of square/rectangular rubberized concrete-filled steel tubes. \textit{Journal of Constructional Steel Research},139: 385 - 396, 2017. \href{https://doi.org/10.1016/j.jcsr.2017.09.006}{DOI: 10.1016/j.jcsr.2017.09.006.}
}

\bitem{
A. Silva, Y. Jiang, J.M. Castro, N. Silvestre, and R. Monteiro. Experimental assessment of the flexural behaviour of circular rubberized concrete-filled steel tubes. \textit{Journal of Constructional Steel Research}, 122: 557 - 570, 2016. \href{https://doi.org/10.1016/j.jcsr.2016.04.016}{DOI: 10.1016/j.jcsr.2016.04.016.}
}

\bitem{
A. Silva, Y. Jiang, L. Macedo, J.M. Castro, R. Monteiro, and N. Silvestre. Seismic performance of composite moment-resisting frames achieved with sustainable cfst members. \textit{Frontiers of Structural and Civil Engineering}, 10(3): 312 - 332, 2016. \href{https://doi.org/10.1007/s11709-016-0345-y}{DOI: 10.1007/s11709-016-0345-y.}
}

\subsection{Conference Papers}

\bitem{
Y. Jiang, B. Kalemi, A. Silva, J.M. Castro, and R. Monteiro. Numerical modelling of circular CFST members and assessment of multi-axial stress state effects. \textit{ce/papers}, 1 (2 - 3): 2128 - 2137, 2017. \href{https://doi.org/10.1002/cepa.258}{DOI: 10.1002/ cepa.258.}
}

\bitem{
A. Silva, Y. Jiang, J.M. Castro, and R. Monteiro. Experimental characterisation of the flexural behaviour of rubberized concrete-filled steel tubular members. \textit{ce/papers}, 1 (2 - 3):2147 - 2156, 2017. \href{https://doi.org/10.1002/cepa.260}{DOI:10.1002 /cepa.260.}
}

\bitem{
Y. Jiang, A. Silva, L. Macedo, J.M. Castro, and R. Monteiro. Numerical modelling of concrete-filled steel tubular members in opensees. \textit{OpenSees Days Europe 2017}, Porto, Portugal, 2017.
}

\bitem{
Y. Jiang, A. Silva, J.M. Castro, R. Monteiro, and N. Silvestre. Experimental and numerical assessment of the behaviour of RuCFST members under monotonic and cyclic bending. \textit{16th World Conference on Earthquake Engineering}, Santiago, Chile, 2017.
}

\bitem{
A. Silva, Y. Jiang, L. Macedo, J.M. Castro, N. Silvestre, and R. Monteiro. Seismic design of composite moment resisting frames with cfst members. \textit{16th World Conference on Earthquake Engineering}, Santiago, Chile,2017.
}

\bitem{
Y. Jiang, A. Silva, J.M. Castro, and R. Monteiro. Experimental assessment of the behaviour of rubberized concrete filled steel tube members. \textit{8th International Conference on Behavior of Steel Structures in Seismic Areas, Shanghai, China}, 2015.
}

\bitem{
Y. Jiang, R. Barros, and J.M. Castro. Opensees as an engine for web-based applications. \textit{OpenSees Days Portugal} 2014, Porto, Portugal, 2014.
}

\end{document}

